Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows

### 2017-03-01 paper.tex
more text

>>>>

One has to be extremely careful in using a narrow-mass search beyond a nominal tolerance of 5 or 10 ppm. 
While it does provide more identifications, a search within say $\pm 3.1$ Daltons should be done with great care.
We only recommend such a search after peaks that correspond to modifications/sequence differences are excluded.
